---
title: "AFR Energy Summit"
author: "Matt Canavan"
date: "11 October 2018"
output:
  xaringan::moon_reader:
    css: ["default", "libs/mjc-css/mjc-theme.css", "libs/mjc-css/mjc-fonts.css"]
    lib_dir: libs
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, dpi = 300, fig.height = 5)

library(knitr)

source("C:/Users/matt/Dropbox/01a. Resources/data/req/req.R")
source("C:/Users/matt/Dropbox/01a. Resources/R/gas/gas.R")
source("C:/Users/matt/Dropbox/01a. Resources/data/energy_data/bp.R")
source("C:/Users/matt/Dropbox/01a. Resources/data/energy_data/hist.R")

```

# We are losing value adding opportunities

``` {r}
p_al_in
```

---

class: inverse, center, middle

---

# More energy means cheaper energy

``` {r}
p_int
```

---

class: inverse, center, middle

---

# QLD CSG is making a difference

``` {r}
p_net_12
```

---

class: inverse, center, middle

---

# Aussie fossil fuels are booming 

``` {r}
p_delta_req
```

---

class: inverse, center, middle

---

# Coal is surging in Asia

``` {r}
p_delta_ap
```

---

class: inverse, center, middle

---

# A lot more coal must be mined

```{r}
p_hist_coal
```

---

# Realistic?

```{r}
p_hist_ipcc
```

---

class: inverse, center, middle

---

# Cleaner fossil fuels can bring down emissions

```{r}
p_last10_p
```

---

class: inverse, center, middle

---

# Coal has helped bring down poverty

```{r }
grid.arrange(p_r_gen$`Asia Pacific` + theme(plot.title = element_text(size = 9), plot.subtitle = element_text(size = 8), plot.caption = element_text(size = 7)), p_pov_ap + theme(plot.title = element_text(size = 9), plot.subtitle = element_text(size = 8), plot.caption = element_text(size = 7)), ncol = 2)
```
